---
title: "Data Import"
output: html_document
Author: Joy Hsu
Date: 2018-09-18
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

#Two Kinds of Paths
1. Absolute: a file or folder’s “full address” on your computer
    * Problematic when another user does not have the same user pathway
1. Relative: directions to a file or folder from your current working directory
    * relative path to the same file as absolute path "./data/FAS_litters.csv"
    
#Import FAS csv files
Import my first csv
```{r}
#Above, example of Relative Path
litters_data = read_csv(file = "./data/FAS_litters.csv")
#janitor takes litters data and cleans up names
litters_data = janitor::clean_names(litters_data)
```


Import pups data
```{r}
pups_data = read_csv(file = "./data/FAS_pups.csv")
pups_data = janitor::clean_names(pups_data)
```

##View Data
```{r}
#shows first 6 rows
head(litters_data)
#Skim summary statistics
skimr::skim(litters_data)
```

#Column Parsing
1. Scans rows to determine type of character
1. Allows shorthand for almost every data type
```{r}
#col_types allows you to define shorthand every data type
litters_data = read_csv(file = "./data/FAS_litters.csv", col_types = "ccddiiii")
litters_data
```
#Other Formats
1. Read in mlb data, excel spreadsheet
1. Use package for read excel
```{r}
#read data using package for read excel
mlb_data = readxl::read_excel(path = "./data/mlb11.xlsx", range = "A1:E17")
#narrow range of cells using range specification
mlb_data = readxl::read_excel(path = "./data/mlb11.xlsx")
#data head
head(mlb_data)
```


















